%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1.5in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}
\begin{letter}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

- Experience in working with tabular data. 
- Experience with spreadsheet software.
- Experience with written communications such as reports, manuscripts, conference abstracts, and grant applications.
- Experience using git for version control.
- Experience in bulk import of files, merging data sets, automated error checking using command line software such as R, bash, python, or OpenRefine.
- Experience in R Programming with R base commands and the R Tidyverse.
- Experience collaborating with others.
Required Education	
Required Licensures, Certifications or other	
Additional Preferred	
- Experience in instructional delivery.
- Experience manipulating regular expressions.
- Experience in data validation.
- Familiarity with agricultural cropping systems.
- Previous experience working with databases.
- Knowledge and experience using regular expressions.
- Ability to work and solve problems independently.
- Effective verbal communication skills.
Physical Requirements	
Working Conditions	
- Remote candidates who are unable to work on campus must have access to a Zoom-capable internet connection.


\quad -- Austin Nathaniel Fife

\thispagestyle{empty}
%----------------------------------------------------------------------------------------

\end{letter}

\end{document}