%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1.5in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}
\begin{letter}
%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------
\\
Dear Members of the Search Committee,\\

My name is Austin Fife and I am writing regarding the position: Biology Post-Doctoral Fellow - 98814

I believe that my background and experience make me a suitable candidate to assist your lab in the analysis of the global phylogeny of Odonata:

I have designed and managed multiple projects simultaneously on the chemical ecology of\\
arthropod-plant-pathogen interactions. Chemical ecology is complex and multidisciplinary
in\\
nature, and accordingly I have collaborated as frequently as possible. I have benefited from\\
the combined expertise of working with over 15 principal investigators from regional universities, state and governmental agencies. These collaborations have permitted me broader experiences\\
in the field and lab, while gaining experience field and lab work.  

My background in scientific computing began during my MSc, when I first learned about R and how to write a thesis in Latex. 5 years later, I now use RStudio daily, along with Git for data cleaning, visualization, and report creation. I also dabble with Anaconda or Linux, and soon hope to learn Python. I have taken specific coursework relating to data science, as seen in my CV. I am also actively seeking opportunities to sharpen my programming skills: I am participating in a 'Bioinformatics and Command Line Tools' workshop, a machine learning bookclub, and a class on impact network analysis at UF. I believe that these data carpentry skills will readily transfer to analyze the multidimensional data your project requires. 

Moving on from technical matters, I also like to emphasize that my previous positions allowed me to share our research with non-technical audiences. While working at Research and Education Centers, I have spoken at 4-H and local rosarian clubs, presented to stakeholders, published technical reports, organized and led educational activities, set up booths and participated in various STEM events designed for the public. I am first author on two publications in peer-reviewed journals. I am finalizing a manuscript in review with ten collaborators, which has been accepted with minor revisions. I expect to finish 2-3 more publications in the near future. I also have spoken at annual meetings by various scientific organizations, in person and online, including oral and poster sessions as described in my CV. I also have experience mentoring other students and temporary personnel, and remote employees as well, instructing them in the proper use of equipment, protocols and standard operating procedures for our lab.

I was raised in northern Idaho, and I am familiar with the surrounding environment, traditions, and many of the flora \& fauna. I also have family living in the region. I believe this familiarity would be a great advantage over other candidates who may need to acclimate to the peculiar environment of Utah. I mention this because postdoctoral studies are notoriously difficult, and a support system is vital during these difficult times to remain productive and produce excellent work. 

In conclusion, I am confident that my expertise in entomology and technical ability in R are well suited for this position.

Thank you for your time and consideration,

\quad -- Austin Nathaniel Fife

\thispagestyle{empty}
%----------------------------------------------------------------------------------------

\end{letter}

\end{document}